\tool: Programmable and Efficient Secure Two-Party Computation for Machine Learning

### 2018-08-07 ndss/pipe.tex
some changes in s5

In this section, we describe our ``secure code partitioning'' technique that
allows \tool to execute programs that require large circuits. The
reason to implement partitioning is as follows: when compiling from a
high level functionality to a circuit, the generated circuits
can quite often be larger than the total memory
available on the machines executing 2PC. The secure protocol for
evaluating this circuit cannot then be generated without swapping the
circuit in and out of main memory, thereby causing large slowdowns
(see Section \ref{sec:pipeeval}). In order to avoid this problem, we
``split'' the high level functionality into smaller programs that
compile into small circuits whose secure evaluation can completely fit
into main memory. These smaller circuits are then evaluated
sequentially to evaluate the entire program. Naturally, care must be
taken to ensure that the partial evaluation of these circuits do not
reveal any more information than the final output of the overall
functionality. More details follow.

Our techniques take inspiration from the idea of pipelining Yao's garbled circuits described in FastGC \cite{yao-pipe}.
However, unlike FastGC, we do not operate at a circuit level and partitioning is independent of the specific
\mpc protocol. 
Let $\prog$ be a program in our source language that
generates a circuit $\crct$. For some programs, the circuit $\crct$
can be larger than
the memory size\footnote{In fact, there is
  an upper limit of $2^{32}-1$ gates for the circuit size in ABY but
  for most machines the memory limit is hit first.} and fail to
execute. Partitioning enables us to 
execute such programs via a source to source transformation that is
oblivious to the underlying \mpc backend. Partitioning decomposes the
program $\prog$ into a sequence of smaller \tool programs
$\progn_1,\progn_2,\ldots,\progn_k$ (as defined below) such
that the circuit size
requirement for each of the $\progn_i$ itself is manageable. We compile
and execute each $\progn_i$ sequentially, feeding the outputs of
$\progn_i$ as state
information to $\progn_{i+1}$. We prove our partitioning scheme to be
correct ($\prog$ and sequential execution of $\progn_1,\progn_2,\ldots,\progn_k$ compute
the same functionality) and secure (sequential execution of
$\progn_1,\progn_2,\ldots,\progn_k$ does
not reveal any more information than $\prog$). 
%
%Prior works such as FastGC \cite{yao-pipe} and ObliVM \cite{oblivm} have developed similar techniques specific to garbled circuits that work at the level of circuits.
%
%considered the idea of pipelining of circuits for secure computation based on Yao's garbled circuits that allows them to scale to large circuits. Our technique of secure code partitioning works with high level programs and does source code transformation. This gives a generic way to execute programs with large underlying circuits (even a mix of arithmetic and Boolean) and is not tied to the specific details of the cryptographic protocol used.
%}
More formal details follow, while an example illustrating the technique of secure code partitioning is provided in the full version. %\appendixref{codepartitioning}.

Let $\prog$ be a program that takes (secret) inputs $x$ from Alice and
$y$ from Bob and produces an output $z$ to both parties. Let
$\prog_1\seq\prog_2\seq\dots\seq\prog_k$ be a decomposition of $\prog$
such that the following holds. Define $\stateq_0 = \bot$ (the public empty
state). For all
$1\leq i\leq k-1$, $\prog_i$ takes inputs $x, y$ and $\stateq_{i-1}$ and
outputs state $\stateq_i$. Finally, $\prog_k$ takes inputs $x, y$ and
$\stateq_{k-1}$ to  output $z$. It is
possible to decompose any program $\prog$  into such
$\prog_1\seq\prog_2\seq\dots\seq\prog_k$. If \tool generates circuit
$\crct_i$ from
$\prog_i$, the parties can execute
$\crct_1, \crct_2, \dots \crct_k$
sequentially (in a distributed setting)  to obtain
$\stateq_1,\dots,\stateq_{k-1},$ and finally output $z$. At the
$i^{\textrm{\tiny{th}}}$ step, the parties only need to store
information proportional to $x,y,\stateq_{i-1}$ and $\crct_i$ (which is
much smaller than $\crct$). However, this execution enables the
parties to learn $\stateq_i$ (for all $1\leq i\leq k-1$), which
completely breaks the security.

>>>>

In this section, we describe our ``secure code partitioning'' technique that
allows \tool to execute programs that require large circuits. The
reason to implement partitioning is as follows: when compiling from a
high level functionality to a circuit, the generated circuits,
especially for ML applications,
can quite often be larger than the total memory
available on the machines executing the 2PC protocol. The secure
protocol for evaluating this circuit cannot then be generated without
swapping the circuit in and out of the main memory, thereby causing large slowdowns
(see Section \ref{sec:pipeeval}). To avoid this problem, we use
partitioning to
``split'' the high level functionality into smaller programs that
compile into small circuits that can completely fit
into the main memory. These small circuits are then evaluated
sequentially, with proper threading of the intermediate outputs, to
evaluate the entire program. Naturally, care must be
taken to ensure that the partial evaluation of these circuits do not
reveal any more information than the final output of the overall
functionality.

Concretely, let $\prog$ be a program in our source language that
generates a circuit $\crct$. For some programs, the circuit $\crct$
can be larger than
the memory size\footnote{In fact, there is
  an upper limit of $2^{32}-1$ gates for the circuit size in ABY but
  for most machines the memory limit is hit first.} and fail to
execute.
%% Partitioning enables us to 
%% execute such programs via a source to source transformation that is
%% oblivious to the underlying \mpc backend.
Partitioning decomposes the
program $\prog$ into a sequence of smaller \tool programs
$\progn_1,\progn_2,\ldots,\progn_k$, as described below, such
that the circuit size
requirement for each of the $\progn_i$ itself is manageable. We compile
and execute each $\progn_i$ sequentially, feeding the outputs of
$\progn_i$ as state
information to $\progn_{i+1}$. We prove our partitioning scheme to be
correct ($\prog$ and sequential execution of $\progn_1,\progn_2,\ldots,\progn_k$ compute
the same functionality) and secure (sequential execution of
$\progn_1,\progn_2,\ldots,\progn_k$ does
not reveal any more information than $\prog$).

Our techniques take inspiration from the idea of pipelining Yao's garbled circuits described in FastGC \cite{yao-pipe}.
However, unlike FastGC, we do not operate at a circuit level and the
scheme itself is independent of the specific
\mpc protocol. 
%
%Prior works such as FastGC \cite{yao-pipe} and ObliVM \cite{oblivm} have developed similar techniques specific to garbled circuits that work at the level of circuits.
%
%considered the idea of pipelining of circuits for secure computation based on Yao's garbled circuits that allows them to scale to large circuits. Our technique of secure code partitioning works with high level programs and does source code transformation. This gives a generic way to execute programs with large underlying circuits (even a mix of arithmetic and Boolean) and is not tied to the specific details of the cryptographic protocol used.
%}
We now describe the instrumentation to ensure the security of the
partitioning scheme.
%More formal details follow, while an example illustrating the technique of secure code partitioning is provided in the full version. %\appendixref{codepartitioning}.

Let $\prog$ takes (secret) inputs $x$ from Alice and
$y$ from Bob and produces an output $z$ to both parties. Let
$\prog_1\seq\prog_2\seq\dots\seq\prog_k$ be a decomposition of $\prog$
such that the following holds. Define $\stateq_0 = \bot$ (the public empty
state). For all
$1\leq i\leq k-1$, $\prog_i$ takes inputs $x, y$ and $\stateq_{i-1}$ and
outputs state $\stateq_i$. Finally, $\prog_k$ takes inputs $x, y$ and
$\stateq_{k-1}$ to  output $z$. It is
possible to decompose any program $\prog$  into such
$\prog_1\seq\prog_2\seq\dots\seq\prog_k$. If \tool generates circuit
$\crct_i$ from
$\prog_i$, the parties can execute
$\crct_1, \crct_2, \dots \crct_k$
sequentially (in a distributed setting)  to obtain
$\stateq_1,\dots,\stateq_{k-1},$ and finally output $z$. At the
$i^{\textrm{\tiny{th}}}$ step, the parties only need to store
information proportional to $x,y,\stateq_{i-1}$ and $\crct_i$ (which is
much smaller than $\crct$). However, this execution enables the
parties to learn $\stateq_i$ (for all $1\leq i\leq k-1$), which
completely breaks the security.
